### 2011-05-12 paper/paper.tex
described the organization of the paper in the introduction

The aim of this paper is to compare the performance in practice of these methods, which we have implemented and tested on high-dimensional convex regions.

\section{The Metropolis Method}

@@

\section{Adaptive Metropolis}

@@

\section{Hit and Run}

@@

\section{Implementation Details}

@@

\section{Results}

@@

\section{Conclusion}

>>>>

The aim of this paper is to compare the performance in practice of these methods, which we have implemented and tested on high-dimensional convex regions. In Sections \ref{metro} and \ref{adapt}, we discuss the Metropolis method in more detail, and introduce a modification which we hope will work better in practice. In Section \ref{hitandrunsection}, we look at the hit-and-run method. Finally, in Sections \ref{implementation} and \ref{results}, we explain our testing and describe the results.

\section{The Metropolis Method}\label{metro}

@@

\section{Adaptive Metropolis}\label{adapt}

@@

\section{Hit and Run}\label{hitandrunsection}

@@

\section{Implementation Details}\label{implementation}

@@

\section{Results}\label{results}

@@

\section{Conclusion}\label{conclusion}
